`mathml`: Translate R Expressions to MathML and LaTeX

### 2023-06-29 rj/mathml.Rmd
math()
small typo

The R\ extension of the markdown language [@Xie2018;@rmarkdown] enables
reproducible statistical reports with nice typesetting in HTML, Microsoft Word,
and LaTeX. Moreover, since recently [@R, version 4.2], R\'s manual pages 
include support for mathematical expressions [@Sarkar2022;@Viechtbauer2022],
which already is a big improvement. However, except for special cases 
such as regression models [@equatiomatic] and R's own plotmath annotation, 
rules for the mapping of built-in language elements to their mathematical 
representation are still lacking. So far, R\ expressions such 
as `pbinom(k, N, p)` are printed as they are and pretty mathematical formulae 
such as \(P_{\mathrm{Bi}}(X \le k; N, p)\) require explicit LaTeX commands
like `P_{\mathrm{Bi}}\left(X \le k; N, p\right)`. Except for very basic use
cases, these commands are tedious to type in and their source code is hard to
read.

>>>>

The R\ extension of the markdown language [@Xie2018;@rmarkdown] enables
reproducible statistical reports with nice typesetting in HTML, Microsoft Word,
and LaTeX. Moreover, since recently [@R, version 4.2], R\'s manual pages 
include support for mathematical expressions [@Sarkar2022;@Viechtbauer2022],
which is already a big improvement. However, except for special cases 
such as regression models [@equatiomatic] and R's own plotmath annotation, 
rules for the mapping of built-in language elements to their mathematical 
representation are still lacking. So far, R\ expressions such 
as `pbinom(k, N, p)` are printed as they are and pretty mathematical formulae 
such as \(P_{\mathrm{Bi}}(X \le k; N, p)\) require explicit LaTeX commands
like `P_{\mathrm{Bi}}\left(X \le k; N, p\right)`. Except for very basic use
cases, these commands are tedious to type in and their source code is hard to
read.
